### 2015-06-07 Paper_english/introduccion.tex
Correcciones Abrstract Introduccion

The video analysis is an essential tool for study and data collection. Tracking reference points is used for calculate position and other associated variables such as speed, acceleration and therefore movement.
The manual tracking of those points can be tedious so it is necessary to have a tool to perform this task automatically. 
Some examples that illustrate these needs are: at \emph{health care level} in the area of \emph{physiotherapy}, \emph{biomechanics academic research},
\emph{measures of performance} in professional sports and \emph{3D animation}.
These examples define use cases with different characteristics, so search for a single solution that covers particular needs of all of them is complex. Have these tools is essential to professional teams needs, whose alternative are high-cost commercial products.\\
\hspace*{0.5cm}This project sought to perform a basic and functional open source video analysis application to provide solution to the above needs, either using an existing open source project as starting point, or developing a prototype software that covers the entire problem generally, to extend the application to other use cases.\\
\hspace*{0.5cm}The system created aims, under certain controlled conditions, to obtain the spatial coordinates from a number of points on a patient. To do this the patient, with a black suit and white markers, is placed in an environment with adequate lighting, then is filmed with multiple cameras over time. This information is brought to the computer and processed to obtain the 3D trayectories of the markers.\\
\hspace*{0.5cm}Working from the algorithm proposed by Herda \cite{herda}, it is proposed a reproducible version from it, containing measures performance on each stage, as well as a methodology for designing a virtual laboratory, developing a complete test system.

>>>>

The video analysis is an essential tool for study and data collection. Tracking reference points can be used to calculate position and other associated variables such as speed, acceleration and therefore movement.
The manual tracking of those points can be tedious so it is necessary to have a tool to perform this task automatically. 
Some examples that illustrate these needs are: at \emph{health care level} in the area of \emph{physiotherapy}, \emph{biomechanics academic research},
\emph{measures of performance} in professional sports and \emph{3D animation}.
These examples define use cases with different characteristics, so the search for a single solution that covers particular needs of all of them is a complex issue. To have these tools is essential for professional teams needs, where other alternatives are high-cost commercial products.\\
\hspace*{0.5cm}This project sought to perform a basic and functional open source video analysis application to provide solution to the above mentioned needs, either using an existing open source project as starting point, or developing a prototype software that covers the entire problem generally, and then extend the application for other use cases.\\
\hspace*{0.5cm}The system created aims, under certain controlled conditions, to obtain the spatial coordinates from a number of points on a subject. To do this the subject, with a black suit and white markers, is placed in an environment with adequate lighting, then filmed with multiple cameras over time. This information is transfered to the computer and processed to obtain the 3D trayectories of all markers.\\
\hspace*{0.5cm}Working from the algorithm proposed by Herda \cite{herda}, it is proposed a reproducible version from it, containing measures of performance on each stage, as well as a methodology for designing a virtual laboratory, developing a complete test system.
